\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-03-19 paper/main.tex
Added selection criteria

\textbf{Libraries.}~\torch~and \tf are popular DL libraries
intensively used in the literature. \jax\ is a newer library that has
been rapidly gaining popularity. All these libraries are open source
with active communities supporting their maintenance.

@@

\Fix{Need to add what labels were used, which period we took the issues from,
how many issues we looked at, define "bug reports", mention how many bugs had 
been filtered with each criterion}

\textbf{Bugs.}~We focused on bug reports that have been accepted by
the developer community as true bugs. We determine this by checking
whether the bugs have appropriate labels and have been fixed with pull
requests linked to them. Among these confirmed bug reports, we choose
the ones that have enough information to reproduce the bugs, i.e.,
code to reproduce the bug, dependencies required for the bug
reproduction
% \Fix{Abid, can you confirm that environment here is not
%   the same as venv-docker that we are using on Table 1? instead it
%   means the version of CUDA, libraries, etc.? If so, avoid (re)using the
%   word environment.}
, clear description of the desired behavior,
etc. Once we can successfully reproduce the bug by creating the
enviroment detailed in the report, we choose the bug to be included in
our dataset.

>>>>

\textbf{Libraries.}~\torch~and \tf are popular DL libraries
intensively used in the literature. \jax\ is a newer library that has
been rapidly gaining popularity. All these libraries are open source
with active communities supporting their maintenance. From these three
libraries, we selected issue reports from specific periods in their
respective issue trackers. For \torch, we selected issues from the
period between \torchfrom and \torchto. For \tf, we selected issues
from the period between \tffrom and \tfto. For \jax, we selected
issues from the period between \jaxfrom and \jaxto. We have chosen
different periods for each library depending on the number of issues
reported in the issue tracker in that period. For example, \tf has a
much longer period compared to the others because the frequency of
issues reported in the issue tracker is lower.

@@

% \Fix{Need to add what labels were used, which period we took the issues from,
% how many issues we looked at, define "bug reports", mention how many bugs had 
% been filtered with each criterion}

\textbf{Bugs.}~We focus on issue reports that have been accepted by
the developer community as true bugs. We determine this by checking
whether the issue reports have the label "bug" and have been fixed with pull
requests linked to them. We then create a filter that incorporates
the periods mentioned above, the label, the issue status being closed
and the presence of a linked pull request. We found \numtorchfiltered{}
issues for \torch, \numtffiltered{} issues for \tf, and \numjaxfiltered{}
issues for \jax after filtering the issues. \torch has the highest number
of issues due to a lack of a label for bugs in the issue tracker.

We then manually inspect the
filtered issues to ensure that they contain enough information to
reproduce the bug, i.e.,
code to reproduce the bug, dependencies required for the bug
reproduction, clear description of the desired behavior,
etc. We also filter bugs that are not in the core functionality
of the library e.g. documentation issues, feature requests, etc.
After this stage of manual inspection, we end up with \numtorchinspected{}
issues for \torch, \numtfinspected{} issues for \tf, and \numjaxinspected{}
issues for \jax.

% Among these confirmed bug reports, we choose
% the ones that have enough information to reproduce the bugs, i.e.,
% code to reproduce the bug, dependencies required for the bug
% reproduction
% \Fix{Abid, can you confirm that environment here is not
%   the same as venv-docker that we are using on Table 1? instead it
%   means the version of CUDA, libraries, etc.? If so, avoid (re)using the
%   word environment.}
% , clear description of the desired behavior,
% etc. 
Afterwards, we assess the reproducibility of the bug by creating a
virtual environment that contains the necessary dependencies to
reproduce the bug.
Once we can successfully reproduce the bug by creating the
enviroment detailed in the report, we choose the bug to be included in
our dataset. Through this process, we end up with \numtorchselected{},
\numtfselected{}, and \numjaxselected{} bug instances for \torch, \tf,
and \jax, respectively.

\Fix{Abid: Added what labels were used, which period we took the issues from,
how many issues we looked at, defined "bug reports", mentioned how many bugs had 
been filtered with each criterion. Please review and revise}
